Titeln på avhandlingens språk

### 2023-03-17 body/part1/chapter2-relatedwork/relatedwork.tex
more related work

Finally,\ \cite{chetoui2022arbench} employed \gls{AR} emulation to evaluate hardware rather than the software implementation itself.
Their tool, \emph{ARBench}, features emulated \gls{AR} workloads that mimic the load placed on the system by real applications.
This approach is similar to the one presented in this dissertation, but it exclusively considers on-device \gls{AR} processing.
Furthermore, the benchmarks are deterministic, and no emulation of realistic human behavior is attempted.

@@

\emph{OpenRTiST}~\cite{george2020openrtist} is a tool for the benchmarking and performance evaluation of Edge Computing deployments using real-time processing of a live video feed.
Video is streamed from a source Android device to a compute node where neural style-transfer~\cite{gatys2016image} is applied to it.
The transformed video is then fed back to the source to be presented, resulting in a compute-intensive, bandwidth-hungry, and latency-sensitive benchmark.

>>>>

Finally, the authors of~\cite{chetoui2022arbench} employ \gls{AR} emulation to evaluate hardware rather than the software implementation itself.
Their tool, \emph{ARBench}, features emulated \gls{AR} workloads that mimic the load placed on the system by real applications.
This approach is similar to the one presented in this dissertation, but it exclusively considers on-device \gls{AR} processing.
Furthermore, the benchmarks are deterministic, and no emulation of realistic human behavior is attempted.

@@

This dissertation complements existing work on benchmarking distributed system architectures.
A rich body of literature exists with examples of such approaches for Cloud computing.
For example, the \gls{YCSB}~\cite{cooper2010benchmarking} is a data-intensive benchmark for the profiling of data centers and cloud services.
Workload characterization in datacenters leads to a similar benchmark in~\cite{jia2013characterizing}.
Both these approaches heavily focus on data processing and downlink transmission in cloud computing scenarios.
In~\cite{turner2012cmart}, the authors introduce \emph{C-MART}, a benchmark for modern web applications running on the cloud.
The benchmark utilizes modern web technologies, can be deployed automatically at a large scale, and include generators which mimic remote clients accessing the system over the internet.\@
\cite{malawski2018benchmarking,back2018using} focus instead on serverless computing, using compute-intensive workloads to benchmark major cloud function providers such as \gls{AWS}, Microsoft Azure, and \gls{GCP}.

A number of works have tackled this challenge in the context of Fog and Edge Computing as well.
\emph{EdgeBench}, introduced in~\cite{das2018edgebench}, corresponds to a benchmarking suite for the Edge.
It emulates three different workloads, speech-to-text, image recognition, and sensor network application traffic, and targets exclusively server and specifically targets serverless deployments.\@
\cite{baurle2022comb} presents \emph{ComB}, a flexible and extensible, application-oriented benchmarking suite for Edge computing.
Its stated purpose is to assist system designers and application developers to evaluate the suitability of Edge deployments.
The framework is designed to decouple orchestration and workload, allowing for easy extension or replacement of the built-in distributed video-analytics benchmark.

\emph{IoTBench}~\cite{lee2019iotbench} is a benchmarking tool for edge-deployed \gls{IOT} applications.
It includes seven representative workloads, and allows researchers to evaluate the performance of these applications on Edge infrastructure through the analysis of computational demands and resource consumption.\@
\cite{mcchesney2019defog} presents a benchmarking suite for the comparison of deployments on the Edge, Fog, or Cloud named \emph{DeFog}.
\emph{DeFog} includes six Fog- and Edge-relevant workloads, including real-time video detection and a text-to-speech application, which are latency-critical and bandwidth-intensive.
In~\cite{lockhart2020scission}, the authors introduce a tool, \emph{Scission}, for the benchmarking of \glspl{DNN} partitioned across the user device, edge, and cloud continuum.
The tool can also be used to automatically determine the optimal partition of a \gls{DNN}.
Finally, \emph{OpenRTiST}~\cite{george2020openrtist} is a tool for the benchmarking and performance evaluation of Edge Computing deployments using real-time processing of a live video feed.
Video is streamed from a source Android device to a compute node where neural style-transfer~\cite{gatys2016image} is applied to it.
The transformed video is then fed back to the source to be presented, resulting in a compute-intensive, bandwidth-hungry, and latency-sensitive benchmark.
